\documentclass[10pt]{article}

\usepackage{latexsym}
\usepackage{etaremune}

\textwidth 15.5cm
\textheight 23.2cm
\topmargin -1cm
\evensidemargin 0in
\oddsidemargin 0in

\newcommand{\voice}[1] { \bigskip \medskip \noindent {\Large \bf #1} \medskip\\ }
\newcommand{\subvoice}[1] { {\large \bf #1} \smallskip\\ }
\newcommand{\emp}[1] { {\em #1}\\ }

\begin{document}

\mbox{\ }
\begin{center}
{\Huge \sc {\bf \vspace{-2.2cm} Curriculum Vitae \\ \vspace{4mm}}
               Rizzi Romeo}\\ \vspace{4mm}
               (January 2022)
\end{center}

\mbox{\ }
\vspace{0.5cm}

\voice{{\LARGE Personal Data}}     
%{\sc Marital Status:} married                                       \\
{\sc Nationality:} Italian                                  \\
%{\sc Place of birth:} Mezzolombardo (Trento-Italy)        \\
{\sc Date of birth:} 20 April 1967                              \\
{\sc Private Address:} via Bolleri $N^o$ 16/1 Martignano --- 38121 (TN)   \\
{\sc Phone Number:} (Italy).3291780915 (cel) \ \ \ (Italy).045.802.7088 (office) \\ 
{\sc e-mail:} {\tt Romeo.Rizzi$@$univr.it}               \\
{\sc Home Page:} {\tt http://profs.sci.univr.it/$\sim$rrizzi}  \\


\vspace{1.8mm}

\voice{{\LARGE Research Interests}}

Combinatorial Optimization.
Algorithms.
Computational Biology.
Computational Complexity.
Operations Research.
Approximation Algorithms.
Distributed Algorithms.
Graphs.
Matroids.
Edge Colorings.
Graph Factorization.
Matching Theory and Problems.
Packing and Covering Problems.
Shortest Paths Problems.
Minimum Cuts.\\


\vspace{1.8mm}
\voice{{\LARGE Education}}

\subvoice{Phd in Computational Mathematics and Informatics}
\emp{Department of Mathematics, Padova University.
September 30, 1997.}

\subvoice{Phd Thesis}
{\sc supervisor:} Prof. Michele Conforti (Department of Mathematics,
                Padova University). \\
{\sc external examiner:} Prof. Bert Gerards (CWI Research Institute, Amsterdam). \\
{\sc title:} Packing $T$-cuts and $T$-joins.\\
{\sc interest areas:} Operations Research, Graph theory, Combinatorics.\\


\subvoice{B.Sc.~Degree in Electronics Engineering}
\emp{Politecnico di Milano. 100/100 cum laude. December 20, 1991.}

\subvoice{B.Sc. Thesis}
{\sc supervisor:} Prof. Francesco Maffioli (Electronics Department,   
                Politecnico di Milano), \\
{\sc title:} The $k$-MST Problem.\\
{\sc interest areas:} Operations Research, Combinatorial Optimization.\\


\vspace{1.8mm}

\voice{{\LARGE Present employment}}

\subvoice{Full Professor by the
          University of Verona}
{\bf december 2019 -- today.}
Sector: Operations Research.

{\bf currently in charge by the department:} Membro della Commissione di valutazione assegni di tutorato per corsi di Informatica e Bioinformatica, Membro della Commissione Ammissione Studenti
Internazionali - Matematica, Referente di Dipartimento per le Olimpiadi dell'informatica, Membro del Collegio dei Docenti del Dottorato Interateneo in Matematica, Membro del Collegio Didattico di Informatica, Membro del Collegio Didattico di Matematica, Membro del Consiglio del Dipartimento di Informatica.

{\bf courses for the deparment:} in Verona,
I held the courses ``Ricerca Operativa''
for the bachelor degree in Applied Mathematics L35 (academic years from 2011-12 up to present)
and ``Algoritmi'' for the master degree in Engineering and Informatics LM18+LM32 (academic years from 2011-12 up to present).
I coordinated and held minicourses for the seminar course ``Math Decisions'' (2014-15, 15-16, 16-17, 17-18) for the master degree in Mathematics LM40. 
For the international degree in Mathematics LM40, the course ``Mathematics for Decisions'' (academic years from 2019-20 up to present); prior to this, I coordinated and held minicourses for the seminar course ``Mathematics for Decisions'' (2014-15, 15-16, 16-17, 17-18, 18-19).
Open to all the students of the department, the course ``Programming Challenges'' (academic years from 2013-14 to 2020-21).
I held classes for highschool teachers in TFA (2012-13, 2014-15) and PAS (2013-14, 2014-15).
I have experimented tandem courses (an offert from the University of Verona to high-school studens) in algorithms.

{\bf further didactical activities:}
Since 2001 I am also active as a trainer and tutor for the Olympiads in Informatics.
In this sector, I have a long and intensive record of activities
which range from classes in high-schools (since 2001) to training and coaching
the italian team (since 2004).\\

\vspace{1.8mm}

\voice{{\LARGE Work Experience}}

\subvoice{Associate Professor by the University of Verona}
{\bf december 2011 -- december 2019.}
Sector: Operations Research.

{\bf in charge by the department:} Presidente di Commissione Paritetica, Membro della Commissione di valutazione assegni di tutorato per corsi di Informatica e Bioinformatica, Referente di Dipartimento per le Olimpiadi dell'informatica, Referente del Dipartimento verso il coderDojo in Verona, Membro del Collegio dei Docenti del Dottorato Interateneo in Matematica, Membro del Collegio Didattico di Informatica, Membro del Collegio Didattico di Matematica, Membro del Consiglio di Corso di Tirocinio Formativo Attivo - TFA classe A042- Informatica, Membro del Consiglio del Dipartimento di Informatica.

{\bf courses for the deparment:} see current employment.\\

\subvoice{Associate Professor by the University of Udine}
{\bf october 2005 -- december 2011.}
Sector: Operations Research.
{\bf (classes)} in Udine,
for the faculty of architectur,
I held the classes ``Ricerca Operativa'' (2006-07, 07-08, 08-09, 09-10), ``Matematica II'' (2005-06, 06-07, 07-08, 08-09),
and ``Matematica'' (2010-11, 2011-2012), for the faculty of enginering I held the classes ``Ricerca Operativa'' (2005-06, 06-07, 07-08, 08-09, 09-10, 10-11, 11-12).
% At the PhD school I taught "Computational Complexity".\\


\subvoice{Assistant Research Professor
          by the Faculty of Science
          at the University of Trento - Italy.}
{\bf march 2001 -- october 2005:}
I taught ``Laboratorio di Algoritmi e Strutture Dati'', ``Algoritmi e Strutture Dati'', ``Complessit\`a Computazionale'', at the master degree, and at the PhD school ``Linear Programming'', ``Computational Molecular Biology''.\\



\subvoice{Researcher at I.R.S.T.}
{\bf August 2000 -- February 2001:}
part of the group CBR (Case Based Reasoning, chief: Paolo Avesani)
of the SRA division
(Automated Reasoning Systems, chief: Paolo Traverso) in IRST.
IRST (Istituto Ricerca Scientifica e Tecnologica)
is part of ITC (Istituto Trentino Cultura)
and is located in Trento - Italy.\\


\subvoice{Post-docs and other temporary positions}
{\bf August 99 -- October 99:}
     Assistant Research Professor at BRICS
     of the University of Aarhus (Denmark). 

\noindent
{\bf April 2000 -- June 2000},
{\bf November 99 -- December 99},
{\bf April 99 -- June 99},
{\bf November 98 -- December 98:}
      I held, for 10 months in total,
      a research position on DONET funds
      at the Research Institute CWI in Amsterdam.
      I was part of the PNA group (Probability, Networks, Algorithms),
      lead and supervised by Professors Alexander Schrijver
      and Bert Gerards.

\noindent
{\bf June 98 -- June 99:}
On a post-doc fellowship
from the University of Padua
spent at the Department of Mathematics
of Padua University.
Supervisor: prof.~Michele Conforti.\\

\subvoice{University teaching}
{\bf Second semester 97/98:}
I taught the course ``Programmazione Combinatoria''
at the Department of Mathematics, Trento University.\\

\subvoice{Activity as a programmer}
{\bf June 97 -- April 98:}
I worked as a programmer
for the Department of Mathematics of the Trento University.\\

\subvoice{Teaching assistant for short degree courses}
{\bf Second semester 96/97:}
Teaching assistant for the class in ``Analisi II''
for the short degree course in Informatics and Automatics
in Rovereto (Trento University).\\

\subvoice{Doctoral fellowship}
{\bf November 93 -- November 96:}
I regularly received the fellowship fund
meant for my Dottorato position and activities
in the Department of Mathematics
of the University of Padova 
under the supervision
and scientific responsibility of Prof.~Conforti.\\

\subvoice{High school teaching (after my degrees)}
I thought into regular state high schools
during the following periods:\\

\begin{center}
\begin{tabular}[c]{||c|p{0.80in}|p{1.25in}|p{1.25in}|p{1.25in}||}
 \hline \hline
  year      & period & school & subject & notes\\
 \hline \hline
  89-90     & {\bf whole year} & I.T.I.S. Hensenberger (Monza)
            & (elettrotecnica) (misure elettriche)
            & before my degrees (only evening classes) \\
% from 14-11-89 to 31-8-90
 \hline \hline
  92-93     & from 21/9/92 to 17/10/92
            & I.T.I. Marconi (Rovereto)
            & (informatica industriale) % code: LIV 
              (matematica applicata) % code: LXIV
            & none \\
  92-93     & from 26/10/92 to 14/11/92 & I.T.C. Martini (Mezzolombardo)
            & 038A (fisica) & none \\
 \hline \hline
  93-94     & from 13/10/93 to 18/11/93 & I.T.I.S. Buonarroti (Trento)
            & 035A (elettrotecnica e applicazioni) & none \\
  93-94     & from 12/2/94 to 26/2/94 & I.T.C. Martini (Mezzolombardo)
            & 048A (matematica applicata) & none \\
 \hline \hline
  95-96     & from 22/9/95 to 6/11/95 & I.T.I.S. Buonarroti (Trento)
            & 035A (elettrotecnica e applicazioni) & 1 day off for competitions\\
 \hline \hline
  96-97   & from 17/4/97 to 21/4/97 & I.P.C. Don Milani (Rovereto)
            & 042A (informatica) & none \\
 \hline \hline
  97-98     & {\bf intero anno scolastico} & I.P.C. Battisti (Trento)
            & 047A (matematica) (matematica ed informatica)
            & none \\
% from 15-9-97 to 30-6-98 con proroga to 31-8-98
 \hline \hline
  98-99   & from 17/9/98 all' 1/10/98 & I.T.C.G. Floriani (Riva)
            & 048A (matematica applicata) & none \\
  98-99   & from 11/1/99 to 11/1/99 & I.T.C.G. Fontana (Rovereto)
            & 047A (matematica) & none \\
 \hline \hline
  99-2000   & from 15/1/00 to 31/3/00 & I.T.I.S. Buonarroti (Trento)
            & 047A (matematica) & none \\
 \hline \hline
\end{tabular}
\end{center}



\vspace{1.8mm}

\voice{{\LARGE Military Service}}

{\bf Performed:} \ \ Enlisted: November 16, 1992.
\ Discharged: November 15, 1993.  \\


\vspace{1.8mm}


\voice{{\LARGE Study and Research abroad}}

   \begin{itemize}
%      \item[] {\bf June -- August 1994:}
%            Cambridge. (England).
%            Just to study English.  
      \item[] {\bf November 1995, October 1996:}
            Guest 
            of Prof.~Andr\'{a}s Seb\"o
            at the Laboratoire
            IMAG % Informatique Mathematiques Appliquees Grenoble 
            and Leibniz of the University of Grenoble, France.
      \item[] {\bf November-December 2000, January--February 2003:}
            Guest 
            of Prof.~Pavol Hell
            at the Department of Mathematics
            of the Simon Fraeser University (SFU)
            of Vancouver, Canada;
            of Prof.~Gary MacGillivray
            by the Department of Mathematics
            of the University of Victoria (UV), Canada
            and of Prof.~Rick Brewster
            by the Department of Computer Science
            of the University of Scherbrook (Montreal), Canada.
      \item[] {\bf August 2001:}
            Guest at BRICS (University of Aarhus, Denmark).
      \item[] {\bf November--December 2004:} 
            Guest
            of Prof.~Pablo Moscato
            by the Bioinformatics Center
            of the University of Newcastle, Australia.
            Visited also the Australian National University in Canberra.
      \item[] {\bf September--October 2005:} 
            Guest
            of Prof.~St\'ephane Vialette
            by l'Universit\'e Paris-Sud (Orsay).
      \item[] {\bf December 2005:} 
            Guest
            of Prof.~Guillaume Fertin
            by l'Universit\'e Nantes.
      \item[] {\bf November 2009:} 
            Invited Professor (``Professor Invitee'') 
            by l'Universit\'e Paris-Est - Marne-la-Vall\'ee
            Invited by Prof.~St\'ephane Vialette.
      \item[] {\bf February 2013:} 
            Invited Professor (``Professor Invitee'') 
            by l'Universit\'e Paris-Est - Marne-la-Vall\'ee
            Invited by Prof.~St\'ephane Vialette.
      \item[] {\bf November 2015:} 
            Invited Professor (``Professor Invitee'') 
            by l'Universit\'e Paris-Est - Marne-la-Vall\'ee
            Invited by Prof.~St\'ephane Vialette.
   \end{itemize}

\vspace{1.8mm}

\voice{{\LARGE Seminars}}

I have promoted the results of my research work
giving seminars at the following institutions (not kept updated list):
Laboratoire IMAG of the CNRS in Grenoble (1995).
Laboratoire Leibniz of the University of Grenoble (1996, 2003).
Istituto IASI del C.N.R. in Roma (1997, 1999),
DEIS dell'Universit\`a di Bologna (1997, 1999, 2001),
DSI dell'Universit\`a di Bologna (2008),
Istituto di Ricerca CWI in Amsterdam (1998),
DEIS del Politecnico di Milano (2000, 2003),
Dip.~Matematica ed Informatica Universit\`a di Udine (2006),
Dipartimento di Informatica della Bicocca di Milano (2003, 2006, 2008),
Dip.~Informatica Universit\`a di Verona (2008),
DSMI dell'Universit\`a di Reggio Emilia (2000),
Istituto IRST dell'ITC di Trento (2000, 2001),
Math. Dept. della Simon Freaser University di Vancouver (2000, 2003),
Math. Dept. della University of Victoria (2003),
Dipartimento di Elettronica del Politecnico di Torino (2003),
Engineering Dept. dell'Universit\`a di New Castle (2004).\\


\newpage

\voice{{\LARGE Publications on International Scientific Journals}}

\input{ListaRivisteInternazionali}

   
\voice{{\LARGE International Conferences with Referee}}

\input{ListaConferenzeInternazionali}



\vspace{1.8mm}

\voice{{\LARGE Chapters in Books}}

\input{ListaCapitoliLibro}


\vspace{1.8mm}

\voice{{\LARGE Books (in Italian, for didactic purposes)}}

\input{ListaLibri}



\vspace{1.8mm}


%\voice{{\LARGE Software Projects}}
%
%\begin{itemize}
%\vspace{-3.0mm}
%  \item[1.] {\sc Romeo Rizzi},
%   \newblock  {\em A simple snark recognizer}.
%   \newblock this is a ``branch and cut'' project under ABACUS, to recognize
%             $3$-graphs whose edges can not be colored with $3$ colors.
%
%  \item[2.] A main theme of LEA group in the Department of Mathematics
%            of Trento University
%            is the realization of ``intertools''
%            available under WEB for the heuristic solution
%            of NP-complete problems.
%            Within such project,
%            I developed the intertool for the
%            ``graph partitioning'' problem.
%
%  \item[3.] {\em Giornalino Virtuale}.
%            This is a project of the Free University of Bozen
%            which has lead the pupils of the several primary schools
%            of Bozen to design, project and create their journal
%            in the web.
%            I have mainly participated to this project
%            in the quality of technician,
%            with the role to assist on informatic issues.
%\end{itemize}

\voice{{\LARGE Honors}}

   - Since 2004, acting as Area Editor for the scientific journal 4OR.

   - Editor of the proceedings of the Oberwolfach meeting
   in Graph Theory, January 2003,
   organized by Reinhard Diestel, Alexander Schrijver
   and Paul D. Seymour.

   - Wrote, together with Prof.~Michele Conforti,
   the review on {\em 4OR} of the masterpiece
   {\em ``Combinatorial Optimization
              - Polyhedra and efficiency''}
   of Alexander Schrijver.

   - Best Paper Award at IPDPS 2002
     for a joint work with Alessandro Mei.

   - Held the class
    ``Algorithmic and Complexity issues in Structure Prediciton and/or Determination''
     at the Third International School on Biology,
     Computation and Information (BCI 2006).
     Dobbiaco (BZ), Italy, September 11-15, 2006.
    %home page della scuola: http://bioinf.dimi.uniud.it/bci2006/

   - Organizer, together with Giuseppe Lancia,
     of an invited session in Computational Biology
     ad AIRO 2005. Camerino.

   - Invited speaker at BioInfoSummer 2004,
     held by the Australian National University in Canberra.

   - Invited speaker at
     ``Workshop on Cycle and Cut Bases'' (2008)
     held at T\"ubingen and inserted in the framework
     SPP 1126 (Algorithmik großer und komplexer Netzwerke).

   - Reviewer of Mathematical Reviews for the American Mathematical Society
     since 2004.

   - Biography included in the 2007 and 2009
     editions of \emph{Who's Who in the World}.

   - Biography included in the 2009/2010 edition
     of \emph{Outstanding Intellectuals of the 21st Century} (IBC, Cambridge).

   - Erd\"os number: 2.

   - As educator, received the following recognizements
     from the \emph{International Biographical Center, Cambridge}:

   \ \ \ - \emph{The Decree of Excellence in Education}.

   \ \ \ - \emph{International Educator of the Year} for 2007 and 2009.

   \ \ \ - \emph{Top 100 Educators} 2008 and 2009.


\vspace{1.2cm}
Verona \hspace{7.8cm} Romeo Rizzi

\end{document}












