\documentclass[10pt]{article}

\usepackage{latexsym}
\usepackage[italian]{babel}
\hyphenation{ra-gio-na-men-to}
\hyphenation{a-stra-zio-ne}
\hyphenation{pro-se-gui-men-to}


\textwidth 15.5cm
\textheight 23.8cm
\topmargin -1.4cm
\evensidemargin 0in
\oddsidemargin 0in

\newcommand{\voice}[1] { \bigskip \medskip \noindent {\Large \bf #1} \medskip\\ }
\newcommand{\subvoice}[1] { {\large \bf #1} \smallskip\\ }
\newcommand{\emp}[1] { {\em #1}\\ }

\begin{document}


\mbox{\ }
\vspace{-2.8cm} 
\begin{center}
{\Huge \sc {\bf My Scientific Publications\\ \vspace{4mm}}
               Rizzi Romeo}\\ \vspace{4mm}
               (december 2003)
\end{center}

\mbox{\ }
\vspace{-0.4cm}


\begin{itemize}
\vspace{-3.0mm}
  \vspace{1.4mm}
  \item {\sc Alessandro Mei, Romeo Rizzi},
   \newblock  Routing Permutations in Partitioned Optical Passive Stars Networks,
   \newblock {\it Journal of Parallel and Distributed Computing}
   \newblock  63 (9) (2003) 847--852.
   \newblock \\ - also accepted at IPDPS 2002 where it received the {\bf Best Paper Award}.
   % report DIT: NO - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Alberto Caprara, Alessandro Panconesi, Romeo Rizzi},
   \newblock  Packing Cycles in Undirected Graphs,
   \newblock {\it Journal of Algorithms}
   \newblock  48 (2003) 239--256.
   \newblock \\ - part of this work was published in the proceedings of ESA 2001.
   \newblock \\ - almost in full also in: Twelfth Annual ACM-SIAM Symposium on Discrete Algorithms (Washington, DC, 2001).
   % report DIT: NO - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Romeo Rizzi},
   \newblock  A Simple Minimum $T$-Cut Algorithm,
   \newblock {\it Discrete Applied Mathematics}
   \newblock  129 (2003) 539--544.
   % report DIT: SI (senza dati rivista) - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Richard C.~Brewster, Romeo Rizzi},
   \newblock  On the complexity of digraph packings,
   \newblock {\it Information Processing Letters}
   \newblock  86 (2) (2003) 101--106.
   %IPL2829
   %online via ScienceDirect:
   %http://www.sciencedirect.com/science?_ob=GatewayURL&_origin=AUGATEWAY&_method=citationSearch&_piikey=S0020019002004787&_version=1&md5=4550693a5fda4e6a7d92fb51803d3114
   % report DIT: NO - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Romeo Rizzi},
   \newblock  On Rajagopalan and Vazirani's $\frac{3}{2}$-Approximation
              Bound for the Iterated $1$-Steiner Heuristic,
   \newblock {\it Information Processing Letters}
   \newblock  86 (6) (2003) 335--338.
   %IPL2862
   %online via ScienceDirect:
   %http://www.sciencedirect.com/science?_ob=GatewayURL&_origin=AUTHORALERT&_method=citationSearch&_piikey=S0020019003002102&_version=1&md5=5603f0c51caeab0a09ec923ed91eccbe
   % report DIT: NO - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Richard C.~Brewster, Pavol Hell, Sarah H.~Pantel, Romeo Rizzi, Anders Yeo},
   \newblock  Packing paths in digraphs,
   \newblock {\it Journal of Graph Theory}
   \newblock  44 (2) (2003) 81--94.
   %Published Online: 2 Sep 2003 DOI: 10.1002/jgt.10126
   % report DIT: NO - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Alberto Caprara, Romeo Rizzi},
   \newblock  Improved Approximation for Breakpoint Graph Decomposition
              and Sorting by Reversals,
   \newblock {\it Journal of Combinatorial Optimization} 6 (2002) 157--182.
   % report DIT: SI - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Romeo Rizzi},
   \newblock  Finding $1$-factors in bipartite regular graphs,
              and edge-coloring bipartite graphs,
   \newblock {\it SIAM Journal on Discrete Mathematics}
   \newblock  15 (3) (2002) 283--288. 
   % report DIT: SI - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Romeo Rizzi},
   \newblock  Minimum $T$-cuts and optimal $T$-pairings,
   \newblock {\it Discrete Mathematics}
   \newblock  257 (1) (2002) 177--181.
   % report DIT: SI - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Alberto Caprara, Romeo Rizzi},
   \newblock  Packing Triangles in Bounded Degree Graphs,
   \newblock {\it Inf. Proc. Lett.} 84 (2002) 175--180.
   % report DIT: SI - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Romeo Rizzi},
   \newblock  Cycle cover property and $CPP=SCC$ property are not equivalent,
   \newblock {\it Discrete Mathematics}
   \newblock  259 (2002) 337--342.
   % report DIT: SI - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Michele Conforti, Romeo Rizzi},  
   \newblock  Shortest Paths in Conservative Graphs,
   \newblock {\it Discrete Mathematics} 226 (2001) 143-153.
   \newblock \\ - part of this work
                  was published in the proceedings of AIRO '96.
   % report DIT: SI - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Romeo Rizzi},
   \newblock  On $4$-connected graphs without even cycle decompositions,
   \newblock {\it Discrete Mathematics} 234 (2001) 181--186.
   % report DIT: SI - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Romeo Rizzi},
   \newblock  On the Recognition of $P_4$-Indifferent Graphs,
   \newblock {\it Discrete Mathematics} 239 (2001) 161-169.
   % report DIT: SI - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Alessandro Panconesi, Romeo Rizzi},
   \newblock  Some Simple Distributed Algorithms for Sparse Networks,
   \newblock {\it Distributed Computing} 14 (2001) 97--100.
   % report DIT: SI - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Romeo Rizzi},
   \newblock  Complexity of Context-free Grammars with Exceptions,
              and the inadequacy of grammars as models for XML and SGML,
   \newblock {\it Markup Languages: Theory and Practice} 3 (1) (2001) 107--116.
   % report DIT: SI - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Romeo Rizzi},
   \newblock  Excluding a simple good pair approach to directed cuts,
   \newblock {\it Graphs and Combinatorics} 17 (2001) 741--744.
   % report DIT: SI - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Romeo Rizzi},
   \newblock  On minimizing symmetric set functions,
   \newblock {\it Combinatorica} 20 (3) (2000) 445--450.
   % report DIT: SI - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Ajai Kapoor, Romeo Rizzi},
   \newblock  Edge-coloring bipartite graphs,
   \newblock {\it Journal of Algorithms} 34 (2) (2000) 390--396.
   % report DIT: SI - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Romeo Rizzi},
   \newblock  A short proof of K\H{o}nig's matching theorem,
   \newblock {\it Journal of Graph Theory} 33 (3) (2000) 138--139.
   % report DIT: SI - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Romeo Rizzi},
   \newblock  A note on range-restricted circuit covers,
   \newblock {\it Graphs and Combinatorics} 16 (2000) 355--358.
   % report DIT: SI - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Romeo Rizzi},
   \newblock  Indecomposable $r$-graphs and some other counterexamples,
   \newblock {\it Journal of Graph Theory} 32 (1) (1999) 1--15.
   % report DIT: SI - POLARIS: SI
 
  \vspace{1.4mm}
  \item {\sc Roberto Battiti, Alan A.~Bertossi, Romeo Rizzi},  
   \newblock  Randomized Greedy Algorithms 
              for the Hypergraph Partitioning Problem,
   \newblock Cap. 2, Vol. 43.
   \newblock Randomized Methods in Algorithm Design.
   \newblock DIMACS: Series in Discrete Mathematics
             and Theoretical Computer Science
   \newblock Pardalos P., Rajasekaran S., Rolim J. (a
 cura di), Providence, RI: American Mathematical Society.
   \newblock 1998. pp. 3-21.
   % report DIT: NO - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Romeo Rizzi},
   \newblock  K\H{o}nig's Edge Coloring Theorem without augmenting paths,
   \newblock {\it Journal of Graph Theory} 29 (1998) 87.
   % report DIT: SI - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Alberto Caprara, Romeo Rizzi},  
   \newblock  Improving a Family of Approximation
              Algorithms to Edge Color Multigraphs,
   \newblock {\it Inf. Proc. Lett.} 68 (1998) 11-15.
   % report DIT: SI - POLARIS: SI

  \vspace{1.4mm}
  \item {\sc Romeo Rizzi},
   \newblock  Impaccando $T$-tagli e $T$-giunti,
   \newblock {\it Bollettino Sezione B dell'Unione Matematica Italiana},
   \newblock {Fascicolo speciale dedicato alle tesi di dottorato}
             (8) 1-A Suppl. (1998) 201-204.
   % report DIT: SI - POLARIS: SI

\end{itemize}

\end{document}

