\begin{etaremune}
  \vspace{-3.0mm}
  \item {\sc Giulia Punzi, Alessio Conte, Roberto Grossi, Romeo Rizzi:}
   \newblock Refined Bounds on the Number of Eulerian Tours in Undirected Graphs,
   \newblock {\it Algorithmica}
   \newblock 86(1) (2024) 194--217.
   
  \item {\sc Alice Raffaele, Romeo Rizzi, Takeaki Uno:}
   \newblock Listing the bonds of a graph in $\tilde{O}(n)$-delay,
   \newblock {\it Discret. Appl. Math.}
   \newblock 348 (2024) 105--121.
   
  \item {\sc Beatrice Amico, Carlo Combi, Romeo Rizzi, Pietro Sala::}
   \newblock Predictive mining of multi-temporal relations,
   \newblock {\it Inf. Comput.}
   \newblock 301 (2024) 105228.
   
  \item {\sc Massimo Cairo, Romeo Rizzi, Alexandru I. Tomescu, Elia C. Zirondelli:}
   \newblock Genome Assembly, from Practice to Theory: Safe, Complete and Linear-Time,
   \newblock {\it ACM Trans. Algorithms}
   \newblock 20(1) (2024) 4:1--4:26.
   
  \item {\sc Manuel Cáceres, Massimo Cairo, Andreas Grigorjew, Shahbaz Khan, Brendan Mumey, Romeo Rizzi, Alexandru I. Tomescu, Lucia Williams:}
   \newblock Width Helps and Hinders Splitting Flows,
   \newblock {\it ACM Trans. Algorithms }
   \newblock 20(2) (2024) 13.
   
  \item {\sc Matteo Zavatteri, Alice Raffaele, Dario Ostuni, Romeo Rizzi:}
   \newblock An interdisciplinary experimental evaluation on the disjunctive temporal problem,
   \newblock {\it Constraints An Int. J.}
   \newblock 28(1) (2023) 1--12.

  \item {\sc Enrico Angelelli, Renata Mansini, Romeo Rizzi:}
   \newblock Solving the probabilistic profitable tour problem on a line,
   \newblock {\it Optim. Lett.}
   \newblock 17(8) (2023) 1873--1888

  \item {\sc Romeo Rizzi, Stéphane Vialette:}
   \newblock On recognising words that are squares for the shuffle product,
   \newblock {\it Theor. Comput. Sci.}
   \newblock  956 (2023) 111156.

  \item {\sc Federica Arrigoni, Andrea Fusiello, Romeo Rizzi, Elisa Ricci:}
   \newblock Revisiting Viewing Graph Solvability: an Effective Approach Based on Cycle Consistency,
   \newblock {\it IEEE Transactions on Pattern Analysis and Machine Intelligence}
   \newblock  (2022) 1--14.
   \newblock  doi: 10.1109/TPAMI.2022.3212595. Online ahead of print.

  \item {\sc Massimo Cairo, Shahbaz Khan, Romeo Rizzi, Sebastian S. Schmidt, Alexandru I. Tomescu:}
   \newblock Safety in s-t Paths, Trails and Walks,
   \newblock {\it Algorithmica}
   \newblock 84(3) (2022) 719--741.

  \item {\sc Matteo Zavatteri, Romeo Rizzi, Tiziano Villa:}
   \newblock Dynamic controllability of temporal networks with instantaneous reaction,
   \newblock {\it Inf. Sci.}
   \newblock 613 (2022) 932--952.

  \item {\sc Manuel Cáceres, Brendan Mumey, Edin Husic, Romeo Rizzi, Massimo Cairo, Kristoffer Sahlin, Alexandru I. Tomescu:}
   \newblock Safety in Multi-Assembly via Paths Appearing in All Path Covers of a DAG,
   \newblock {\it IEEE ACM Trans. Comput. Biol. Bioinform.}
   \newblock 19(6) (2022) 3673--3684.

  \item {\sc Massimo Cairo, Shahbaz Khan, Romeo Rizzi, Sebastian S. Schmidt, Alexandru I. Tomescu, Elia C. Zirondelli:}
   \newblock A simplified algorithm computing all s-t bridges and articulation points,
   \newblock {\it Discret. Appl. Math.}
   \newblock 305 (2021) 103--108.

  \item {\sc Carlo Combi, Romeo Rizzi, Pietro Sala:}
   \newblock Checking Sets of Pure Evolving Association Rules,
   \newblock {\it Fundam. Informaticae}
   \newblock 178(4) (2021) 283--313.

  \item {\sc Matteo Zavatteri, Carlo Combi, Romeo Rizzi, Luca Viganò:}
   \newblock Consistency checking of STNs with decisions: Managing temporal and access-control constraints in a seamless way,
   \newblock {\it Inf. Comput.}
   \newblock 280 (2021) 104637.

  \item {\sc Laurent Bulteau, Guillaume Fertin, Anthony Labarre, Romeo Rizzi, Irena Rusu:}
   \newblock Decomposing subcubic graphs into claws, paths or triangles,
   \newblock {\it J. Graph Theory}
   \newblock 98(4) (2021) 557--588.

  \item {\sc Sara Giuliani, Zsuzsanna Lipták, Francesco Masillo, Romeo Rizzi:}
   \newblock When a dollar makes a BWT,
   \newblock {\it Theor. Comput. Sci.}
   \newblock 857 (2021) 123--146.

  \item {\sc Vicente Acuña, Roberto Grossi, Giuseppe Francesco Italiano, Leandro Lima, Romeo Rizzi, Gustavo Sacomoto, Marie-France Sagot, Blerina Sinaimeri:}
   \newblock On Bubble Generators in Directed Graphs,
   \newblock {\it Algorithmica}
   \newblock 82(4) (2020) 898--914.

  \item {\sc Carlo Comin, Anthony Labarre, Romeo Rizzi, Stéphane Vialette:}
   \newblock Sorting with forbidden intermediates,
   \newblock {\it Discret. Appl. Math.}
   \newblock  279 (2020) 49--68.

  \item {\sc Massimo Cairo, Carlo Comin, Romeo Rizzi:}
   \newblock Instantaneous reaction-time in dynamic consistency checking of conditional simple temporal networks,
   \newblock {\it J. Log. Algebraic Methods Program.}
   \newblock  113 (2020) 100542.

  \item {\sc Pietro Sala, Carlo Combi, Matteo Mantovani, Romeo Rizzi:}
   \newblock Discovering Evolving Temporal Information: Theory and Application to Clinical Databases,
   \newblock {\it SN Comput. Sci.}
   \newblock 1(3) (2020) 153.

\end{etaremune}
