\begin{etaremune}
  \vspace{-3.0mm}
  
  \item {\sc Enrico Fraccaroli, Francesco Stefanni, Romeo Rizzi, Davide Quaglia, Franco Fummi:}
   \newblock Network Synthesis for Distributed Embedded Systems,
   \newblock {\it IEEE Trans. on Computers}
   \newblock 67(9) (2018) 1315--1330.
   % DOI:10.1109/TC.2018.2812797.

  \item {\sc Carlo Comin, Romeo Rizzi:}
   \newblock Checking dynamic consistency of conditional hyper temporal networks via mean payoff games: Hardness and (pseudo) singly-exponential time algorithm,
   \newblock {\it Inf. Comput.}
   \newblock 259(3) (2018) 348--374.

  \item {\sc Carlo Comin, Romeo Rizzi:}
    \newblock An Improved Upper Bound on Maximal Clique Listing via Rectangular Fast Matrix Multiplication
    \newblock {\it Algorithmica}
    \newblock 80(12) (2018) 3525--3562.
   
  \item {\sc Alessio Conte, Roberto Grossi, Andrea Marino, Romeo Rizzi:}
   \newblock Efficient enumeration of graph orientations with sources,
   \newblock {\it Discrete Applied Mathematics}
   \newblock 246 (2018) 22--37.

  \item {\sc Ademir Hujdurovic, Edin Husic, Martin Milanicw, Romeo Rizzi, Alexandru I. Tomescu:}
   \newblock Perfect Phylogenies via Branchings in Acyclic Digraphs and a Generalization of Dilworth's Theorem,
   \newblock {\it ACM Trans. Algorithms}
   \newblock 14(2) (2018) 20:1--20:26.

  \item {\sc Carlo Comin, Romeo Rizzi:}
   \newblock Improved Pseudo-polynomial Bound for the Value Problem and Optimal Strategy Synthesis in Mean Payoff Games,
   \newblock {\it Algorithmica}
   \newblock 77(4) (2017) 995--1021.

  \item {\sc Carlo Comin, Roberto Posenato, Romeo Rizzi:}
   \newblock Hyper temporal networks - A tractable generalization of simple temporal networks and its relation to mean payoff games,
   \newblock {\it Constraints}
   \newblock 22(2) (2017) 152--190.

  \item {\sc Franca Rinaldi, Romeo Rizzi:}
   \newblock Solving the train marshalling problem by inclusion-exclusion,
   \newblock {\it Discrete Applied Mathematics}
   \newblock 217 (2017) 685--690.

  \item {\sc Liliana Alcón, Marisa Gutierrez, István Kovács, Martin Milanic, Romeo Rizzi:}
   \newblock Strong cliques and equistability of EPT graphs,
   \newblock {\it Discrete Applied Mathematics}
   \newblock 203 (2016) 13--25.

  \item {\sc Both Emerite Neou, Romeo Rizzi, Stéphane Vialette:}
   \newblock Permutation Pattern matching in $(213, 231)$-avoiding permutations,
   \newblock {\it Discrete Mathematics \& Theoretical Computer Science}
   \newblock  18(2) (2016)
   
  \item {\sc David Cariolaro, Romeo Rizzi:}
   \newblock On the Complexity of Computing the Excessive $[B]$-Index of a Graph,
   \newblock {\it Journal of Graph Theory}
   \newblock 82(1) (2016) 65--74.

  \item {\sc Stefano Benati, Romeo Rizzi, Craig A. Tovey:}
   \newblock The complexity of power indexes with graph restricted coalitions,
   \newblock {\it Mathematical Social Sciences}
   \newblock 76 (2015) 53--63.

  \item {\sc Romeo Rizzi, Florian Sikora:}
   \newblock Some Results on More Flexible Versions of Graph Motif,
   \newblock {\it Theory Comput. Syst.}
   \newblock 56(4) (2015) 612--629.

  \item {\sc Alexandru I. Tomescu, Travis Gagie, Alexandru Popa, Romeo Rizzi, Anna Kuosmanen, Veli Mäkinen:}
   \newblock Explaining a Weighted DAG with Few Paths for Solving Genome-Guided Multi-Assembly,
   \newblock {\it IEEE/ACM Trans. Comput. Biology Bioinform.}
   \newblock 12(6) (2015) 1345--1354.

  \item {\sc Ferdinando Cicalese, Martin Milanic, Romeo Rizzi:}
   \newblock On the complexity of the vector connectivity problem,
   \newblock {\it Theor. Comput. Sci.}
   \newblock 591 (2015) 60--71.        

  \item {\sc Alberto Caprara, Mauro Dell'Amico, Jos\'e Carlos D\'\i{}az, Manuel Iori, Romeo Rizzi:}
   \newblock Friendly bin packing instances without Integer Round-up Property,
   \newblock {\it Math. Program.}
   \newblock  150(1) (2015) 5--17.

  \item {\sc Laurent Bulteau, Guillaume Fertin, Romeo Rizzi, St\'ephane Vialette:}
   \newblock  Some algorithmic results for [2]-sumset covers,
   \newblock {\it  Inf. Process. Lett.}
   \newblock  115(1) (2015) 1--5.

  \item {\sc Romeo Rizzi, David Cariolaro:}
   \newblock  Polynomial Time Complexity of Edge Colouring Graphs with Bounded Colour Classes,
   \newblock {\it Algorithmica}
   \newblock   69(3) (2014) 494--500.

  \item {\sc Romeo Rizzi, Alexandru I.~Tomescu, Veli M\"akinen:}
   \newblock  On the complexity of Minimum Path Cover with Subpath Constraints for multi-assembly,
   \newblock {\it  BMC Bioinformatics}
   \newblock  15(S--9) (2014) S5.

  \item {\sc Bostjan Bresar, Tanja Gologranc, Martin Milanic, Douglas F. Rall, Romeo Rizzi:}
   \newblock  Dominating sequences in graphs,
   \newblock {\it  Discrete Mathematics}
   \newblock  336 (2014) 22--36.

  \item {\sc Marien Abreu, Domenico Labbate, Romeo Rizzi, John Sheehan:}
   \newblock  Odd 2-factored snarks,
   \newblock {\it  Eur. J. Comb.}
   \newblock  36 (2014) 460--472.

  \item {\sc Guillaume Blin, Paola Bonizzoni, Riccardo Dondi, Romeo Rizzi, Florian Sikora:}
   \newblock  Complexity insights of the Minimum Duplication problem,
   \newblock {\it  Theor. Comput. Sci.}
   \newblock  530 (2014) 66--79.

  \item {\sc Martin Milanic, Romeo Rizzi, Alexandru I.~Tomescu:}
   \newblock  Set graphs. II. Complexity of set graph recognition and similar problems,
   \newblock {\it Theor. Comput. Sci.}
   \newblock   547 (2014) 70--81. 

  \item {\sc Alexandru I.~Tomescu, Anna Kuosmanen, Romeo Rizzi, Veli M\"akinen:}
   \newblock  A novel min-cost flow method for estimating transcript expression with RNA-Seq,
   \newblock {\it BMC Bioinformatics}
   \newblock   14(S-5) (2013) S15. 

  \item {\sc Guillaume Blin, Romeo Rizzi, Florian Sikora, St\'ephane Vialette:}
   \newblock  Minimum Mosaic Inference of a Set of Recombinants,
   \newblock {\it  Int. J. Found. Comput. Sci.}
   \newblock  24(1) (2013) 51--66.

  \item {\sc Romeo Rizzi, Alexandru I.~Tomescu:}
   \newblock  Ranking, unranking and random generation of extensional acyclic digraphs,
   \newblock {\it Inf. Process. Lett.}
   \newblock   113(5--6) (2013) 183--187. 

  \item {\sc Guillaume Blin, Romeo Rizzi, St\'ephane Vialette:}
   \newblock  A Faster Algorithm for Finding Minimum Tucker Submatrices,
   \newblock {\it  Theory Comput. Syst.}
   \newblock  51(3) (2012) 270--281.

  \item {\sc Romeo Rizzi, Luca Nardin:}
   \newblock  Polynomial Time Instances for the IKHO Problem,
   \newblock {\it ISRN Electronics}
   \newblock  2012, 10 pages (2012).

  \item {\sc Giulia Galbiati, Romeo Rizzi, Edoardo Amaldi:}
   \newblock  On the approximability of the minimum strictly fundamental cycle basis problem,
   \newblock {\it Discrete Applied Mathematics}
   \newblock  159(4) (2011) 187--200.

  \item {Marcin Kubica, Romeo Rizzi, St\'ephane Vialette, Tomasz Walen:}
   \newblock Approximation of RNA multiple structural alignment,
   \newblock {\it J. Discrete Algorithms}
   \newblock 9(4) (2011) 365--376.

  \item {\sc Paola Bonizzoni, Gianluca Della Vedova, Riccardo Dondi, Yuri Pirola, Romeo Rizzi:}
   \newblock  Pure Parsimony Xor Haplotyping,
   \newblock {\it IEEE/ACM Transactions on Computational Biology and Bioinformatics}
   \newblock  7(4) (2010) 598--609.

  \item {\sc David Cariolaro, Romeo Rizzi:}
   \newblock  Excessive factorizations of bipartite multigraphs,
   \newblock {\it Discrete Applied Mathematics}
   \newblock  158 (2010) 1760--1766.

  \item {\sc Ga\"elle Brevier, Romeo Rizzi, St\'ephane Vialette:}
   \newblock   Complexity issues in color-preserving graph embeddings,
   \newblock   {\it Theor. Comput. Sci.}
   \newblock    411(4-5) (2010) 716--729.

  \item {\sc Guillaume Fertin, Danny Hermelin, Romeo Rizzi, St\'ephane Vialette:}
   \newblock  Finding common structured patterns in linear graphs,
   \newblock {\it Theor. Comput. Sci.}
   \newblock 411(26--28) (2010) 2475--2486.

  \item {\sc Romeo Rizzi, Pritha Mahata, Luke Mathieson, Pablo Moscato:}
   \newblock  Hierarchical Clustering Using the Arithmetic-Harmonic Cut: Complexity and Experiments,
   \newblock {\it PLoS ONE}
   \newblock 5(12) (2010) .

  \item {\sc Romeo Rizzi:}
   \newblock   Minimum Weakly Fundamental Cycle Bases Are Hard To Find,
   \newblock {\it Algorithmica}
   \newblock 53(3) (2009) 402--424.

  \item {\sc Telikepalli Kavitha, Christian Liebchen, Kurt Mehlhorn, Dimitrios Michail, Romeo Rizzi, Torsten Ueckerdt, Katharina Anna Zweig:}
   \newblock  Cycle bases in graphs characterization, algorithms, complexity, and applications,
   \newblock   {\it Computer Science Review}
   \newblock   3(4) (2009) 199--243.

  \item {\sc Alan A.~Bertossi, Cristina M.~Pinotti, Romeo Rizzi:}
   \newblock  Optimal receiver scheduling algorithms for a multicast problem,
   \newblock {\it Discrete Applied Mathematics}
   \newblock  157(15) (2009) 3187--3197.

  \item {\sc Peter Biro, David Manlove, Romeo Rizzi:}
   \newblock   Maximum weight cycle packing in directed graphs, with application to kidney exchange programs,
   \newblock {\it Discrete Mathematics, Algorithms and Applications}
   \newblock  1(4) (2009) 499--517.

  \item {\sc Guillaume Fertin, Romeo Rizzi, St\'ephane Vialette:}
   \newblock  Finding Occurrences of Protein
              Complexes in Protein-Protein Interaction Graphs,
   \newblock {\it Journal of Discrete Algorithms}
   \newblock 7(1) (2009) 90--101.

  \item {\sc Ekkehard K\"ohler, Christian Liebchen, Gregor W\"unsch, Romeo Rizzi:}
   \newblock  Lower bounds for strictly fundamental cycle bases in grid graphs.    \newblock {\it Networks}
   \newblock 53(2) (2009) 191--205.

  \item {\sc Stefano Benati, Romeo Rizzi:}
   \newblock   The optimal statistical median of a convex set of arrays,
   \newblock {\it Journal of Global Optimization}
   \newblock 44(1) (2009) 79--97.

  \item {\sc Romeo Rizzi:}
   \newblock   Approximating the Maximum $3$-Edge-Colorable Subgraph Problem,
   \newblock {\it Discrete Mathematics}
   \newblock  309(12) (2009) 4164--4168.

  \item {\sc Richard C.~Brewster, Pavol Hell, Romeo Rizzi:}
   \newblock  Oriented star packings,
   \newblock {\it Journal of Combinatorial Theory, Series~B}
   \newblock  98 (2008) 558--576.

  \item {\sc Giuseppe Lancia, R.~Ravi, Romeo Rizzi:}
   \newblock  Haplotyping for Disease Association: A Combinatorial Approach, 
   \newblock {\it IEEE Transactions on Computational Biology and Bioinformatics}
   \newblock  5(2) (2008) 245--251.

  \item {\sc Danny Hermelin, Dror Rawitz, Romeo Rizzi, St\'ephane Vialette:}
   \newblock  The Minimum Substring Cover Problem,
   \newblock {\it Information and Computation}
   \newblock 206(11) (2008) 1303--1312.

  \item {\sc Reuven Cohen, Liran Katzir, Romeo Rizzi:}
   \newblock   On the Trade-off Between Energy and Multicast Efficiency in 802.16e-like Mobile Networks,
   \newblock {\it IEEE Transactions on Mobile Computing}
   \newblock  7(3) (2008) 346--357.
%   \newblock \\ - a previous version,
%                  with only Reuven Cohen and Romeo Rizzi as authors,
%                  was also accepted at Infocom~2006.

  \item {\sc Giuseppe Lancia, Franca Rinaldi, Romeo Rizzi:}
   \newblock  Flipping letters to minimize the support of a string,
   \newblock  {\it International Journal of Foundations of Computer Science}
   \newblock  19(1) (2008) 5--17.

  \item {\sc Guillaume Blin, Cedric Chauve, Guillaume Fertin, Romeo Rizzi, St\'ephane Vialette:}
   \newblock  Comparing Genomes with Duplications: A Computational Complexity Point of View.
   \newblock  {\it IEEE/ACM Trans. Comput. Biology Bioinform.}
   \newblock  4(4) (2007) 523--534.

  \item {\sc Michael Elkin, Christian Liebchen, Romeo Rizzi:}
   \newblock  New length bounds for cycle bases,
   \newblock {\it Information Processing Letters}
   \newblock  104(5) (2007) 186--193.

  \item {\sc Francesco Maffioli, Romeo Rizzi, Stefano Benati:}
   \newblock  Least and most colored bases,
   \newblock {\it Discrete Applied Mathematics}
   \newblock  155(15) (2007) 1958--1970.

  \item {\sc Stephen Finbow, Andrew King, Gary MacGillivray, Romeo Rizzi:}
   \newblock  The firefighter problem for graphs of maximum degree three,
   \newblock {\it Discrete Mathematics}
   \newblock  307(16) (2007) 2094--2105.

  \item {\sc Christian Liebchen, Romeo Rizzi:}
   \newblock  Classes of cycle bases,
   \newblock {\it Discrete Applied Mathematics}
   \newblock  155 (2007) 337--355.
  % gia inserito nel 2006

  \item {\sc Stefano Benati, Romeo Rizzi:}
   \newblock  A mixed integer linear programming formulation
              of the optimal mean/Value-at-Risk portfolio problem,
   \newblock {\it European Journal of Operational Research}
   \newblock  176 (2007) 423--434.
  % gia inserito nel 2006

  \item {\sc Alessandro Mei, Romeo Rizzi:}
   \newblock  Online Permutation Routing in
              Partitioned Optical Passive Star Networks,
   \newblock {\it IEEE Trans. Computers}
   \newblock  55(12) (2006) 1557--1571.

  \item {\sc Alessandro Mei, Romeo Rizzi:}
   \newblock  Hypercube Computations on Partitioned Optical
              Passive Stars Networks,
   \newblock {\it IEEE Trans. Parallel Distrib. Syst.}
   \newblock  17(6) (2006) 497--507.
%   \newblock \\ - a preliminary version appeared in: HiPC 2003, 95--104.

  \item {\sc Romeo Rizzi:}
   \newblock  Acyclically Pushable Bipartite Permutation Digraphs: an algorithm,
   \newblock {\it Discrete Mathematics}
   \newblock 306(12) (2006) 1177--1188.

  \item {\sc Romeo Rizzi, Marco Rospocher:}
   \newblock  Covering partially directed graphs with directed paths,
   \newblock {\it Discrete Mathematics}
   \newblock 306(13) (2006) 1390--1404.

  \item {\sc Giuseppe Lancia, Romeo Rizzi:}
   \newblock  A polynomial case of the parsimony haplotyping problem,
   \newblock {\it Oper. Res. Lett.}
   \newblock  34(3) (2006) 289--295.

  \item {\sc Guillaume Blin, Guillaume Fertin, Romeo Rizzi,
                  St\'ephane Vialette:}
   \newblock What Makes the Arc-Preserving Subsequence Problem Hard?
   \newblock  {\it Transactions on Computational Systems Biology II}
   \newblock  LNCS vol.~3680 (2005) 1--36.
%   \newblock \\ - a draft version of this work appeared on:
%                  International Conference on Computational Science (2) 2005: 860-868.

  \item {\sc Vineet Bafna, Sorin Istrail, Giuseppe Lancia, Romeo Rizzi:}
   \newblock  Polynomial and APX-hard cases of the Individual Haplotyping Problem,
   \newblock {\it Theoretical Computer Science}
   \newblock  335(1) (2005) 109--125.
%   \newblock \\ - a previous related work by the same authors
%               ``SNPs Problems: Complexity and Practical Algorithms''
%              was also accepted at WABI 2002.

  \item {\sc Zhi-Zhong Chen, Tao Jiang, Guohui Lin, Romeo Rizzi,
                  Jianjun Wen, Dong Xu, Ying Xu:}
   \newblock  More Reliable Protein NMR Peak Assignment via Improved $2$-Interval Scheduling,
   \newblock {\it Journal of Computational Biology}
   \newblock 12(2) 2005 129--146.

  \item {\sc Christian Liebchen, Romeo Rizzi:}
   \newblock  A greedy approach to compute a minimum cycle basis
              of a directed graph,
   \newblock {\it Information Processing Letters}
   \newblock  94(3) (2005) 107--112.
   %IPL3233
   %online via ScienceDirect:
   %http://authors.elsevier.com/TrackMyPaper.html?add_art=myarticles&trk_article=IPL3233&trk_mail=on&trk_surname=Liebchen

  \item {\sc Mauro Cettolo, Michele Vescovi, Romeo Rizzi:}
   \newblock  Evaluation of BIC-based algorithms for audio segmentation,
   \newblock {\it Computer Speech \& Language}
   \newblock 19(2) (2005) 147--170.
%   \newblock Volume 19, Issue 2, April (2005) pages 147-170
%   \newblock \\ - a previous work by the same authors
%                ``A DP Algorithm for Speaker Change Detection'',
%               a starting point for this subsequent work,
%               had been accepted at Eurospeech 2003.

  \item {\sc Elia~Ardizzoni, Alan A.~Bertossi, Maria Cristina Pinotti,
                  Shashank Ramaprasad,  Romeo Rizzi,  Madhusudana V.S. Shashanka:}
   \newblock  Optimal Skewed Data Allocation on Multiple Channels with Flat
              Broadcast per Channel,
   \newblock {\it IEEE Transactions on Computers}
   \newblock  54(5) (2005) 558--572.

  \item {\sc A.A. Bertossi, M.C. Pinotti, R. Rizzi, P. Gupta:} % Phalguni Gupta 
   \newblock  Allocating Servers in Infostations for Bounded Simultaneous Requests,
   \newblock {\it Journal of Parallel and Distributed Computing}
   \newblock  64 (2004) 1113--1126.
%   \newblock \\ - also accepted at IEEE Int'l Parallel and Distributed Processing Symposium, 2003.

  \item {\sc Alan A.~Bertossi, Cristina M.~Pinotti, Romeo Rizzi, Anil M.~Shende:}
   \newblock  Channel Assignment for Interference Avoidance in Honeycomb Wireless Networks,
   \newblock {\it Journal of Parallel and Distributed Computing}
   \newblock  64 (2004) 1329--1344.

  \item {\sc Alberto Caprara, Andrea Lodi, Romeo Rizzi:}
   \newblock  On $d$-Threshold Graphs and $d$-Dimensional Bin Packing,
   \newblock {\it Networks}
   \newblock  44(4) (2004) 266--280.
%   \newblock \\ - also accepted at 2003 Optimization Days.

  \item {\sc Alberto Caprara, Alessandro Panconesi, Romeo Rizzi:}
   \newblock  Packing Cuts in Graphs,
   \newblock {\it Networks}
   \newblock  44(1) (2004) 1--11.
%   \newblock \\ - part of this work was published in the proceedings of ESA 2001.

  \item {\sc Giuseppe Lancia, Maria Cristina Pinotti, Romeo Rizzi:}
   \newblock  Haplotyping Populations by Pure Parsimony: Complexity, 
              Exact, and Approximation Algorithms,
   \newblock {\it INFORMS J.~on Comp.}
   \newblock  16(4) (2004) 348--359.

  \item {\sc Michele Conforti, Romeo Rizzi:}  
   \newblock  Combinatorial Optimization
              - Polyhedra and efficiency: A book review,
   \newblock {\it 4OR}
   \newblock 2(2) (2004) 153--159.

  \item {\sc Alberto Caprara, Alessandro Panconesi, Romeo Rizzi:}
   \newblock  Packing Cycles in Undirected Graphs,
   \newblock {\it Journal of Algorithms}
   \newblock  48(1) (2003) 239--256.
%   \newblock \\ - part of this work was published in the proceedings of ESA 2001.
   % report DIT: NO - POLARIS: SI

  \item {\sc Romeo Rizzi:}
   \newblock  On Rajagopalan and Vazirani's $\frac{3}{2}$-Approximation
              Bound for the Iterated $1$-Steiner Heuristic,
   \newblock {\it Information Processing Letters}
   \newblock  86(6) (2003) 335--338.
   %IPL2862
   %online via ScienceDirect:
   %http://www.sciencedirect.com/science?_ob=GatewayURL&_origin=AUTHORALERT&_method=citationSearch&_piikey=S0020019003002102&_version=1&md5=5603f0c51caeab0a09ec923ed91eccbe
   % report DIT: NO - POLARIS: SI

  \item {\sc Alessandro Mei, Romeo Rizzi:}
   \newblock  Routing Permutations in Partitioned Optical Passive Stars Networks,
   \newblock {\it Journal of Parallel and Distributed Computing}
   \newblock  63(9) (2003) 847--852.
   \newblock \\ - also accepted at IPDPS 2002 where it received the {\bf Best Paper Award}.
   % report DIT: NO - POLARIS: SI

  \item {\sc Richard C.~Brewster, Romeo Rizzi:}
   \newblock  On the complexity of digraph packings,
   \newblock {\it Information Processing Letters}
   \newblock  86(2) (2003) 101--106.
   %IPL2829
   %online via ScienceDirect:
   %http://www.sciencedirect.com/science?_ob=GatewayURL&_origin=AUGATEWAY&_method=citationSearch&_piikey=S0020019002004787&_version=1&md5=4550693a5fda4e6a7d92fb51803d3114
   % report DIT: NO - POLARIS: SI

  \item {\sc Romeo Rizzi:}
   \newblock  A Simple Minimum $T$-Cut Algorithm,
   \newblock {\it Discrete Applied Mathematics}
   \newblock  129 (2003) 539--544.
   % report DIT: SI (senza dati rivista) - POLARIS: SI

  \item {\sc Richard C.~Brewster, Pavol Hell, Sarah H.~Pantel, Romeo Rizzi, Anders Yeo:}
   \newblock  Packing paths in digraphs,
   \newblock {\it Journal of Graph Theory}
   \newblock  44(2) (2003) 81--94.
   %Published Online: 2 Sep 2003 DOI: 10.1002/jgt.10126
   % report DIT: NO - POLARIS: SI

  \item {\sc Romeo Rizzi:}
   \newblock  Cycle cover property and $CPP=SCC$ property are not equivalent,
   \newblock {\it Discrete Mathematics}
   \newblock  259 (2002) 337--342.
   % report DIT: SI - POLARIS: SI

  \item {\sc Alberto Caprara, Romeo Rizzi:}
   \newblock  Packing Triangles in Bounded Degree Graphs,
   \newblock {\it Information Processing Letters}
   \newblock  84(4) (2002) 175--180.
   % report DIT: SI - POLARIS: SI

  \item {\sc Romeo Rizzi:}
   \newblock  Minimum $T$-cuts and optimal $T$-pairings,
   \newblock {\it Discrete Mathematics}
   \newblock  257(1) (2002) 177--181.
   % report DIT: SI - POLARIS: SI

  \item {\sc Romeo Rizzi:}
   \newblock  Finding $1$-factors in bipartite regular graphs,
              and edge-coloring bipartite graphs,
   \newblock {\it SIAM Journal on Discrete Mathematics}
   \newblock  15(3) (2002) 283--288. 
   % report DIT: SI - POLARIS: SI

  \item {\sc Alberto Caprara, Romeo Rizzi:}
   \newblock  Improved Approximation for Breakpoint Graph Decomposition
              and Sorting by Reversals,
   \newblock {\it Journal of Combinatorial Optimization}
   \newblock  6 (2002) 157--182.
   % report DIT: SI - POLARIS: SI

  \item {\sc Romeo Rizzi:}
   \newblock  Complexity of Context-free Grammars with Exceptions,
              and the inadequacy of grammars as models for XML and SGML,
   \newblock {\it Markup Languages: Theory and Practice}
   \newblock  3(1) (2001) 107--116.
   % report DIT: SI - POLARIS: SI

  \item {\sc Alessandro Panconesi, Romeo Rizzi:}
   \newblock  Some Simple Distributed Algorithms for Sparse Networks,
   \newblock {\it Distributed Computing}
   \newblock  14 (2001) 97--100.
   % report DIT: SI - POLARIS: SI

  \item {\sc Romeo Rizzi:}
   \newblock  On the Recognition of $P_4$-Indifferent Graphs,
   \newblock {\it Discrete Mathematics}
   \newblock  239 (2001) 161--169.
   % report DIT: SI - POLARIS: SI

  \item {\sc Romeo Rizzi:}
   \newblock  On $4$-connected graphs without even cycle decompositions,
   \newblock {\it Discrete Mathematics}
   \newblock  234 (2001) 181--186.
   % report DIT: SI - POLARIS: SI

  \item {\sc Romeo Rizzi:}
   \newblock  Excluding a simple good pair approach to directed cuts,
   \newblock {\it Graphs and Combinatorics}
   \newblock  17 (2001) 741--744.
   % report DIT: SI - POLARIS: SI

  \item {\sc Michele Conforti, Romeo Rizzi:}  
   \newblock  Shortest Paths in Conservative Graphs,
   \newblock {\it Discrete Mathematics}
   \newblock  226 (2001) 143--153.
%   \newblock \\ - part of this work
%                  was published in the proceedings of AIRO '96.
   % report DIT: SI - POLARIS: SI

  \item {\sc Romeo Rizzi:}
   \newblock  A note on range-restricted circuit covers,
   \newblock {\it Graphs and Combinatorics}
   \newblock  16 (2000) 355--358.
   % report DIT: SI - POLARIS: SI

  \item {\sc Romeo Rizzi:}
   \newblock  On minimizing symmetric set functions,
   \newblock {\it Combinatorica}
   \newblock  20(3) (2000) 445--450.
   % report DIT: SI - POLARIS: SI

  \item {\sc Romeo Rizzi:}
   \newblock  A short proof of K\H{o}nig's matching theorem,
   \newblock {\it Journal of Graph Theory}
   \newblock  33(3) (2000) 138--139.
   % report DIT: SI - POLARIS: SI

  \item {\sc Ajai Kapoor, Romeo Rizzi:}
   \newblock  Edge-coloring bipartite graphs,
   \newblock {\it Journal of Algorithms}
   \newblock  34(2) (2000) 390--396.
   % report DIT: SI - POLARIS: SI

  \item {\sc Romeo Rizzi:}
   \newblock  Indecomposable $r$-graphs and some other counterexamples,
   \newblock {\it Journal of Graph Theory}
   \newblock  32(1) (1999) 1--15.
   % report DIT: SI - POLARIS: SI

  \item {\sc Alberto Caprara, Romeo Rizzi:}  
   \newblock  Improving a Family of Approximation
              Algorithms to Edge Color Multigraphs,
   \newblock {\it Information Processing Letters}
   \newblock  68(1) (1998) 11--15.
   % report DIT: SI - POLARIS: SI

  \item {\sc Romeo Rizzi:}
   \newblock  K\H{o}nig's Edge Coloring Theorem without augmenting paths,
   \newblock {\it Journal of Graph Theory}
   \newblock  29 (1998) 87.

\end{etaremune}
