
\begin{etaremune}
\vspace{-3.0mm}

  \item {\sc Alan A.~Bertossi, Cristina M.~Pinotti, Romeo Rizzi:}
   \newblock  Data Broadcasts on Multiple Wireless Channels:
Exact and Time-Optimal Solutions for Uniform Data
and Heuristics for Non-Uniform Data,
   \newblock  Updated Chapter~73 for the Second Edition of:
               Handbook of Approximation Algorithms and Metaheuristics
   \newblock (T.F. Gonzalez, Editor),
   \newblock Vol~I: Basic Methodologies and Techniques
   \newblock  Taylor \& Francis Books (CRC Press),
   \newblock Chapman \& Hall/CRC, Boca Raton, 2017, pp.~73.1--73.16.
%  \newblock ISBN: 

  \item {\sc Alan A.~Bertossi, Cristina M.~Pinotti, Romeo Rizzi, Phalguni Gupta:}
   \newblock  Scalable algorithms for server allocation in infostations,
   \newblock  Chapter~27 in:
               Handbook of Research on Scalable Computing Technologies
   \newblock (K-C. Li, C-H. Hsu, L.T.~Yang, J.~Dongarra, H.~Zima Editors),
   \newblock  IGI Global,
   \newblock 2008.
%  \newblock ISBN: 978-1-60566-661-7; 1,086 pp; 645--658, July 2009

  \item {\sc Alan A.~Bertossi, Cristina M.~Pinotti, Romeo Rizzi:}
   \newblock  Scheduling data broadcasts on wireless channels:
               exact solutions and heuristics,
   \newblock  Chapter~73 in:
               Handbook of Approximation Algorithms and Metaheuristics
   \newblock (T.F. Gonzalez, Editor),
   \newblock  Taylor \& Francis Books (CRC Press),
   \newblock Chapman \& Hall/CRC, Boca Raton, 2007, pp.~73.1--73.16.
%  \newblock ISBN: 978-1-58488-550-4

  \item {\sc Alan A.~Bertossi, Cristina M.~Pinotti, Romeo Rizzi, Anil M.~Shende:}
   \newblock  Channel assignment in honeycomb networks,
   \newblock Theoretical computer science,  150--162,
   \newblock Lecture Notes in Comput. Sci., 2841,
   \newblock Springer, Berlin, 2003.

  \item {\sc Roberto Battiti, Alan A.~Bertossi, Romeo Rizzi:}  
   \newblock  Randomized Greedy Algorithms 
              for the Hypergraph Partitioning Problem,
   \newblock Cap.~2, Vol.~43.
   \newblock Randomized Methods in Algorithm Design.
   \newblock DIMACS: Series in Discrete Mathematics
             and Theoretical Computer Science
   \newblock Pardalos P., Rajasekaran S., Rolim J. (a cura di),
             Providence, RI: American Mathematical Society.
   \newblock 1998. pp. 3-21.

\end{etaremune}
