
\begin{etaremune}
  \item {\sc Laurent Bulteau, Romeo Rizzi, Stéphane Vialette},
   \newblock Pattern Matching for $k$-Track Permutations,
   \newblock IWOCA 2018.
   \newblock 102--114 (2018)

  \item {\sc Alessio Conte, Roberto Grossi, Andrea Marino, Romeo Rizzi, Luca Versari},
   \newblock Listing Subgraphs by Cartesian Decomposition,
   \newblock MFCS 2018.
   \newblock 84:1--84:16 (2018)

  \item {\sc Alessio Conte, Roberto Grossi, Andrea Marino, Romeo Rizzi, Takeaki Uno, Luca Versari},
   \newblock Tight Lower Bounds for the Number of Inclusion-Minimal $st$-Cuts,
   \newblock WG 2018.
   \newblock 100--110 (2018)
   
  \item {\sc M.~Cairo, P.~Medvedev, N.O.~Acosta, R.~Rizzi, A.I.~Tomescu},
   \newblock Optimal Omnitig Listing for Safe and Complete Contig Assembly,
   \newblock CPM 2017.
   \newblock 29:1--29:12 (2017)

  \item {\sc M.~Cairo, R.~Rizzi},
   \newblock The Complexity of Simulation and Matrix Multiplication,
   \newblock SODA 2017.
   \newblock 2203--2214 (2017)

  \item {\sc M.~Cairo, R.~Rizzi},
   \newblock Dynamic Controllability Made Simple,
   \newblock TIME 2017.
   \newblock 8:1--8:16 (2017)

  \item {\sc M.~Cairo, C.~Combi, C.~Comin, L.~Hunsberger, R.~Posenato, R.~Rizzi, Matteo Zavatteri},
   \newblock Incorporating Decision Nodes into Conditional Simple Temporal Networks,
   \newblock TIME 2017.
   \newblock 9:1--9:18 (2017)

  \item {\sc M.~Cairo, L.~Hunsberger, R.~Posenato, R.~Rizzi},
   \newblock A Streamlined Model of Conditional Simple Temporal Networks - Semantics and Equivalence Results,
   \newblock TIME 2017.
   \newblock 10:1--10:19 (2017)

  \item {\sc V.~Acu\~na, R.~Grossi, G.F.~Italiano, L.~Lima, R.~Rizzi, G.~Sacomoto, M-F. Sagot, B.~Sinaimeri},
   \newblock On Bubble Generators in Directed Graphs,
   \newblock  WG 2017.
   \newblock  18--31 (2017)

  \item {\sc A.~Hujdurovic, E.~Husic, M.~Milanic, R.~Rizzi, A.I.~Tomescu},
   \newblock The Minimum Conflict-Free Row Split Problem Revisited,
   \newblock  WG 2017.
   \newblock  303--315 (2017)

  \item {\sc M.~Cairo, G.~Farina, R.~Rizzi},
   \newblock Decoding Hidden Markov Models Faster Than Viterbi Via Online Matrix-Vector (max, +)-Multiplication,
   \newblock AAAI 2016
   \newblock 1484--1490 (2016)

  \item {\sc C.~Comin, A.~Labarre, R.~Rizzi, S.~Vialette},
   \newblock Sorting with Forbidden Intermediates,
   \newblock AlCoB 2016.
   \newblock 133--144 (2016)

  \item {\sc A.~Kuosmanen, A.~Sobih, R.~Rizzi, V.~Mäkinen, A.I.~Tomescu},
   \newblock On using Longer RNA-seq Reads to Improve Transcript Prediction Accuracy,
   \newblock BIOINFORMATICS 2016.
   \newblock 272--277 (2016)

  \item {\sc L.~Bulteau, G.~Fertin, A.~Labarre, R.~Rizzi, I.~Rusu},
   \newblock Decomposing Cubic Graphs into Connected Subgraphs of Size Three,
   \newblock COCOON 2016.
   \newblock 393--404 (2016)

  \item {\sc A.~Conte, R.~Grossi, A.~Marino, R.~Rizzi, L.~Versari},
   \newblock Directing Road Networks by Listing Strong Orientations,
   \newblock IWOCA 2016.
   \newblock 83--95 (2016)

  \item {\sc A.~Conte, R.~Grossi, A.~Marino, R.~Rizzi},
   \newblock Listing Acyclic Orientations of Graphs with Single and Multiple Sources,
   \newblock LATIN 2016.
   \newblock 319--333 (2016)

  \item {\sc A.~Farinelli, G.~Franco, R.~Rizzi},
   \newblock Minimal Multiset Grammars for Recurrent Dynamics,
   \newblock Int. Conf. on Membrane Computing 2016.
   \newblock 177--189 (2016)

  \item {\sc M.~Cairo, R.~Grossi, R.~Rizzi},
   \newblock New Bounds for Approximating Extremal Distances in Undirected Graphs,
   \newblock SODA 2016.
   \newblock 363--376 (2016)

  \item {\sc B.E.~Neou, R.~Rizzi, S.~Vialette},
   \newblock Pattern Matching for Separable Permutations,
   \newblock SPIRE 2016.
   \newblock 260--272 (2016)

  \item {\sc M.~Cairo, C.~Comin, R.~Rizzi},
   \newblock Instantaneous Reaction-Time in Dynamic-Consistency Checking of Conditional Simple Temporal Networks,
   \newblock TIME 2016.
   \newblock 80--89 (2016)

  \item {\sc M.~Cairo, R.~Rizzi},
   \newblock Dynamic Controllability of Conditional Simple Temporal Networks Is PSPACE-complete,
   \newblock TIME 2016.
   \newblock 90--99 (2016)

  \item {\sc A.~Conte, R.~Grossi, A.~Marino, R.~Rizzi},
   \newblock Enumerating Cyclic Orientations of a Graph,
   \newblock IWOCA 2015.
   \newblock 88--99 (2015)

  \item {\sc C.~Comin, R.~Rizzi},
   \newblock Dynamic Consistency of Conditional Simple Temporal Networks via Mean Payoff Games: A Singly-Exponential Time DC-checking,
   \newblock TIME 2015.
   \newblock 19--28 (2015).

  \item {\sc C.~Combi, R.~Rizzi, P.~Sala},
   \newblock The Price of Evolution in Temporal Databases,
   \newblock TIME 2015.
   \newblock 47--58 (2015).

  \item {\sc R.~Rizzi, G.~Sacomoto, M-F.~Sagot},
   \newblock Efficiently Listing Bounded Length st-Paths,
   \newblock IWOCA 2014.
   \newblock 318--329 (2014).

  \item {G.~Bacci, M.~Miculan, R.~Rizzi},
   \newblock Finding a Forest in a Tree - The Matching Problem for Wide Reactive Systems,
   \newblock TGC 2014.
   \newblock 17--33 (2014).

  \item {R.A.~Ferreira, R.~Grossi, R.~Rizzi, G.~Sacomoto, M-F.~Sagot},
   \newblock Amortized $\tilde{O}(|V|)$-Delay Algorithm for Listing Chordless Cycles in Undirected Graphs,
   \newblock ESA 2014.
   \newblock 418--429 (2014).

  \item {R.~Rizzi, A.I.~Tomescu},
   \newblock Faster FPTASes for Counting and Random Generation of Knapsack Solutions,
   \newblock ESA 2014.
   \newblock 762--773 (2014).

  \item {G.~Blin, P.~Morel, R.~Rizzi, S.~Vialette},
   \newblock Towards Unlocking the Full Potential of Multileaf Collimators,
   \newblock SOFSEM 2014.
   \newblock 138--149 (2014).

  \item {C.~Comin, R.~Rizzi, R.~Posenato},
   \newblock A Tractable Generalization of Simple Temporal Networks and Its Relation to Mean Payoff Games,
   \newblock TIME 2014.
   \newblock 7--16 (2014).

  \item {R.~Rizzi, S.~Vialette},
   \newblock On Recognizing Words That Are Squares for the Shuffle Product,
   \newblock CSR 2013: 8th International Computer Science Symposium in Russia.
   \newblock LNCS~7913: 235--245 (2013).

  \item {E.~Birmel\'e, R.A.~Ferreira, R.~Grossi, A.~Marino, N.~Pisanti, R.~Rizzi, G.~Sacomoto},
   \newblock Optimal Listing of Cycles and st-Paths in Undirected Graphs,
   \newblock SODA 2013.
   \newblock SIAM: 1884--1896 (2013).

  \item {F.~Cicalese, T.~Gagie, E.~Giaquinta, E.S.~Laber, Z.~Lipt\'ak, R.~Rizzi, A.I.~Tomescu},
   \newblock Indexes for Jumbled Pattern Matching in Strings, Trees and Graphs,
   \newblock SPIRE 2013.
   \newblock 56--63 (2013).

  \item {R.~Rizzi, R.~Posenato},
   \newblock Optimal Design of Consistent Simple Temporal Networks,
   \newblock TIME 2013.
   \newblock 19--25 (2013).

  \item {A.I.~Tomescu, A.~Kuosmanen, R.~Rizzi, V.~M\"akinen},
   \newblock A Novel Combinatorial Method for Estimating Transcript Expression with RNA-Seq: Bounding the Number of Paths,
   \newblock WABI 2013.
   \newblock 85--98 (2013).

\vspace{-1.8mm}
  \item {R.~Rizzi, F.~Sikora},
   \newblock Some Results on more Flexible Versions of Graph Motif,
   \newblock CSR 2012: 7th International Computer Science Symposium in Russia.
   \newblock LNCS~7353: 278--289 (2012).

\vspace{-1.8mm}
  \item {D.~Hermelin, R.~Rizzi, S.~Vialette},
   \newblock Algorithmic Aspects of the Intersection and Overlap Numbers of a Graph,
   \newblock ISAAC 2012: Algorithms and Computation - 23rd International Symposium
   \newblock LNCS~7676: 465--474 (2012).

\vspace{-1.8mm}
  \item {G.~Blin, P.~Bonizzoni, R.~Dondi, R.~Rizzi, F.~Sikora},
   \newblock Complexity Insights of the Minimum Duplication Problem,
   \newblock SOFSEM 2012: Theory and Practice of Computer Science.
   \newblock LNCS~7147: 153--164 (2012).

\vspace{-1.8mm}
  \item {X.~Yang, F.~Sikora, G.~Blin, S.~Hamel, R.~Rizzi, S.~Aluru},
   \newblock An Algorithmic View on Multi-Related-Segments: A Unifying Model for Approximate Common Interval,
   \newblock TAMC 2012: Theory and Applications of Models of Computation - 9th Annual Conference.
   \newblock LNCS~7287: 319--329 (2012).

\vspace{-1.8mm}
  \item {G.~Blin, R.~Rizzi, S.~Vialette},
   \newblock A Polynomial-Time Algorithm for Finding a Minimal Conflicting Set Containing a Given Row,
   \newblock CSR 2012: 6th International Computer Science Symposium in Russia.
   \newblock LNCS~6651: 373--384 (2011).

\vspace{-1.8mm}
  \item {E.~Amaldi, C.~Iuliano, R.~Rizzi},
   \newblock On cycle bases with limited edge overlap,
   \newblock CTW 2011: Proceedings of the 10th Cologne-Twente Workshop on graphs and combinatorial optimization
   \newblock http://ctw2011.dia.uniroma3.it/ctw\_proceedings.pdf\#page=64: 52--55 (2011).

\vspace{-1.8mm}
  \item {R.A.~Ferreira, R.~Grossi, R.~Rizzi},
   \newblock Output-Sensitive Listing of Bounded-Size Trees in Undirected Graphs,
   \newblock 19th Annual European Symposium on Algorithms (ESA 2011).
   \newblock LNCS~6942: 275--286 (2011).

\vspace{-1.8mm}
  \item {E.~Amaldi, C.~Iuliano, R.~Rizzi},
   \newblock Efficient Deterministic Algorithms for Finding a Minimum Cycle Basis in Undirected Graphs,
   \newblock Integer Programming and Combinatorial Optimization, 14th International Conference (IPCO 2010)
   \newblock LNCS~6080: 397--410 (2010).
%
%\vspace{-1.8mm}
%  \item {P.~Bonizzoni, G.~Della Vedova, R.~Dondi, Y.~Pirola, R.~Rizzi},
%   \newblock Pure Parsimony Xor Haplotyping,
%   \newblock  CoRR abs\/1001.1210 (2010).

\vspace{-1.8mm}
  \item {G.~Blin, R.~Rizzi, S.~Vialette},
   \newblock A Faster Algorithm for Finding Minimum Tucker Submatrices,
   \newblock 6th Conference on Computability in Europe (CiE 2010).
   \newblock LNCS~6158: 69--77 (2010).

\vspace{-1.8mm}
  \item {E.~Amaldi, C.~Iuliano, T.~Jurkiewicz, K.~Mehlhorn, R.~Rizzi},
   \newblock Breaking the $O(m^2n)$ Barrier for Minimum Cycle Bases,
   \newblock 17th Annual European Symposium on Algorithms (ESA 2009).
   \newblock LNCS~5757: 301--312 (2009).

\vspace{-1.8mm}
  \item {P.~Bonizzoni, G.~Della Vedova, R.~Dondi, Y.~Pirola, R.~Rizzi},
   \newblock Pure Parsimony Xor Haplotyping,
   \newblock Bioinformatics Research and Applications, 5th International Symposium (ISBRA 2009).
   \newblock LNCS~5542: 186--197 (2009).

\vspace{-1.8mm}
  \item {G.~Fertin, D.~Hermelin, R.~Rizzi, S.~Vialette},
   \newblock Common Structured Patterns in Linear Graphs: Approximations and Combinatorics,
   \newblock 18th Symposium on Combinatorial Pattern Matching (CPM'07).
   \newblock LNCS~4580: 241--252 (2007).

\vspace{-1.8mm}
  \item {G.~Brevier, R.~Rizzi, S.~Vialette},
   \newblock Pattern Matching in Protein-Protein Interaction Graphs,
   \newblock 16th International Symposium on Fundamentals
              of Computation Theory (FCT 2007).
   \newblock LNCS~4639: 137--148 (2007).

\vspace{-1.8mm}
  \item {D.~Hermelin, D.~Rawitz, R.~Rizzi, S.~Vialette},
   \newblock The Minimum Substring Cover Problem,
   \newblock In, Christos Kaklamanis, Martin Skutella, editors,
   \newblock 5th Workshop on Approximation and Online Algorithms (WAOA'07).
   \newblock LNCS~4927: 170--183 (2007).

\vspace{-1.8mm}
  \item {C.~Liebchen, G.~W\"unsch, E.~K\"ohler, A.~Reich, R.~Rizzi},
   \newblock Benchmarks for Strictly Fundamental Cycle Bases,
   \newblock WEA 2007.
   \newblock LNCS~4525: 365--378 (2007).

\vspace{-1.8mm}
  \item {M.~Kubica, R.~Rizzi, S.~Vialette, T.~Wale\'n},
   \newblock Approximation of RNA Multiple Structural Alignment,
   \newblock 17th Symposium on Combinatorial Pattern Matching (CPM'06).
   \newblock LNCS~4009: 211--222 (2006).

\vspace{-1.8mm}
  \item {G.~Lancia, F.~Rinaldi, R.~Rizzi},
   \newblock Flipping letters to minimize the support of a string,
   \newblock in The Prague Stringology Conference, PSC06,
   \newblock Stringology 9--17 (2006).

\vspace{-1.8mm}
  \item {\sc R.~Cohen, R.~Rizzi},
   \newblock   On the Trade-Off Between Energy and Multicast Efficiency in 802.16e-Like Mobile Networks,
   \newblock INFOCOM 2006.

\vspace{-1.8mm}
  \item {C.~Chauve, G.~Fertin, R.~Rizzi, S.~Vialette},
   \newblock Genomes containing duplicates are hard to compare,
   \newblock Int. Workshop on Bioinformatics Research and Applications (IWBRA).
   \newblock LNCS~3992: 783--790 (2006).

\vspace{-1.8mm}
  \item {M.~Dalpasso, G.~Lancia and R.~Rizzi},
   \newblock The String Barcoding Problem is NP-Hard,
   \newblock in RECOMB Satellite on Comparative Genomics, (A.~Mc Lyshag and D.~Huson eds),
   \newblock Lecture Notes in Bioinformatics, Springer, 85--93, (2005). 

\vspace{-1.8mm}
  \item {G.~Fertin, R.~Rizzi, S.~Vialette},
   \newblock Finding Exact and Maximum Occurrences
of Protein Complexes in Protein-Protein Interaction Graphs,
   \newblock International Symposium on Mathematical Foundations of Computer Science (MFCS'05).
   \newblock LNCS~3618: 328--339 (2005).

\vspace{-1.8mm}
  \item {A.~Mei, R.~Rizzi},
   \newblock Online Permutation Routing in Partitioned Optical Passive Star Networks,
   \newblock CoRR abs/cs/0502093. (2005).

\vspace{-1.8mm}
  \item {G.~Blin, G.~Fertin, R.~Rizzi, S.~Vialette},
   \newblock What Makes the Arc-Preserving Subsequence Problem Hard?
   \newblock 5th Int. Workshop on Bioinformatics Research and Applications (IWBRA'05).
   \newblock  LNCS~3515: 860--868 (2005).

\vspace{-1.8mm}
  \item {G.~Blin, R.~Rizzi},
   \newblock Conserved Interval Distance Computation Between Non-trivial Genomes,
   \newblock COCOON 2005.
   \newblock  LNCS~3595: 22--31 (2005).

\vspace{-1.8mm}
  \item {G.~Lancia, R.~Rizzi},
   \newblock Combinatorial Problems Arising in the Analysis of Human Polymorphisms,
   \newblock AIRO 2005, Camerino, 2005.

\vspace{-1.8mm}
  \item {G.~Lancia, F.~Rinaldi, R.~Rizzi},
   \newblock Reducing the k-mer diversity of a string,
   \newblock AIRO 2004, Lecce, 2004.

\vspace{-1.8mm}
  \item {G.~Blin, G.~Fertin, R.~Rizzi, S.~Vialette},
   \newblock Pattern Matching in Arc-Annotated Sequences: New Results for the APS Problem,
   \newblock 5th Journ\'ees Ouvertes de Biologie, Informatique et Math\'ematiques (JOBIM'04).
   \newblock Montr\'eal, Quebec. 2004.
   \newblock IEEE Computer Society.

\vspace{-1.8mm}
  \item {E.~Ardizzoni, A.A.~Bertossi, M.C.~Pinotti, R.~Rizzi},
   \newblock Comparing Algorithms for Data Broadcasting over Multiple Channels,
   \newblock Algorithms for Wirelss and Ad-hoc networks (ASWAN),
   \newblock Boston, USA, August 2004.

\vspace{-1.8mm}
  \item {A.A.~Bertossi, M.C.~Pinotti, S.~Ramaprasad, R.~Rizzi, M.V.S.~Shashanka},
   \newblock Optimal multi-channel data allocation with flat broadcast per channel,
   \newblock IEEE Int’l Parallel and Distributed Processing Symposium (IPDPS),
   \newblock Santa Fe, April 2004.

\vspace{-1.8mm}
  \item {Z-Z.~Chen, T.~Jiang, G.-H. Lin, R.~Rizzi, J.~Wen, D.~Xu, Y.~Xu},
   \newblock More Reliable Protein NMR Peak Assignment via Improved 2-Interval Scheduling,
   \newblock ESA 2003.
   \newblock LNCS~2832: 580-592 (2003).

\vspace{-1.8mm}
  \item {M.~Cettolo, M.~Vescovi, R.~Rizzi},
   \newblock  A DP Algorithm  for Speaker Change Detection,
   \newblock Eurospeech 2003.

\vspace{-1.8mm}
  \item {A.~Mei, R.~Rizzi},
   \newblock Mapping Hypercube Computations onto Partitioned Optical Passive Star Networks,
   \newblock HiPC.
   \newblock  LNCS~2913: 95--104 (2003).

\vspace{-1.8mm}
  \item {S.~Finbow, A.~King, G.~MacGillivray, R.~Rizzi},
   \newblock The Firefighter Problem for Graphs of Maximum Degree Three,
   \newblock EuroComb'03.

\vspace{-1.8mm}
  \item {A.A.~Bertossi, M.C.~Pinotti, R.~Rizzi, A.M.~Shende},
   \newblock Channel Assignment in Honeycomb Networks,
   \newblock 3rd ICTCS,
   \newblock Bertinoro, Italy, October 2003.

\vspace{-1.8mm}
  \item {A.A.~Bertossi, M.C.~Pinotti R.~Rizzi},
   \newblock Channel Assignment with Separation on Trees and Interval Graphs,
   \newblock 3rd Int’l Workshop on Wireless, Mobile and Ad Hoc Networks,
   \newblock (satellite workshop of IEEE IPDPS 2003),
   \newblock April 2003.

\vspace{-1.8mm}
  \item {A.A.~Bertossi, M.C.~Pinotti, R.~Rizzi, P.~Gupta},
   \newblock Allocating Servers in Infostations for Bounded Simultaneous Requests,
   \newblock IEEE Int’l Parallel and Distributed Processing Symposium (IPDPS),
   \newblock Nice, April 2003.

\vspace{-1.8mm}
  \item {A.A.~Bertossi, M.C.~Pinotti, R.~Rizzi},
   \newblock Channel assignment on strongly-simplicial graphs,
   \newblock IEEE WMAN,
   \newblock Nice, April 2003.

\vspace{-1.8mm}
  \item {R.~Rizzi, V.~Bafna, S.~Istrail, and G.~Lancia},
   \newblock Practical Algorithms and Fixed-parameter Tractability
   \newblock of the Single Individual SNP Haplotyping Problem,
   \newblock 2nd Workshop on Algorithms in Bioinformatics (WABI),
   \newblock LNCS 2452: 29--43, 2002.

\vspace{-1.8mm}
  \item {A.~Mei, R.~Rizzi},
   \newblock Routing Permutations in Partitioned Optical Passive Star Networks,
   \newblock IPDPS 2002.

\vspace{-1.8mm}
  \item {A.~Caprara, A.~Panconesi, R.~Rizzi},
   \newblock  Packing Cycles and Cuts in Undirected Graphs,
   \newblock ESA 2001.
   \newblock LNCS 2161: 512--523 (2001).

\vspace{-1.8mm}
  \item {R.~Rizzi},
   \newblock On minimizing symmetric set functions,
   \newblock Fourth Slovene International Conference
             in Graph Theory, 1999.

\vspace{-1.8mm}
  \item {M.~Conforti, R.~Rizzi},
   \newblock Shortest Paths in Conservative Graphs,
   \newblock AIRO '96, Perugia, 1996.

\end{etaremune}
